Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-14 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add Atallah reference (rain dist'n)

Given the its high resolution and consistancy with rain gage values, [@Villarini2011] recommends the use of Stage IV precipitation data for the analysis of rainfall distribution in landfalling tropical cyclones. However, the Stage IV dataset only provides data since 2001 [@Lin2005] and is therefore inadequate for use in this analysis.

@@

In comparison to the storm track, the areas of extreme rain and extreme wind can vary. For example, storms undergoing an extratropical transition can bring heavy rains to the left of the storm's center track, while extreme winds are more common to the right of the track [@Halverson2015, @Grabich2016].

>>>>

Given its high resolution and consistancy with rain gage values, [@Villarini2011] recommends the use of Stage IV precipitation data for the analysis of rainfall distribution in landfalling tropical cyclones. However, the Stage IV dataset only provides data since 2001 [@Lin2005] and is therefore inadequate for use in this analysis.

NLDAS does not provide information on precipitation over the ocean, preventing its use in assessing the develpment of the storm prior to landfall [@Villarini2011]. This point is moot for this analysis.

@@

In comparison to the storm track, the areas of extreme rain and extreme wind can vary. For example, storms undergoing an extratropical transition can bring heavy rains to the left of the storm's center track, while extreme winds are more common to the right of the track [@Halverson2015, @Grabich2016]. In contrast, storm that interact with a downstream ridge tend to bring heavy rains to the right of the storm's center track [@Atallah2007].
